Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-11 method.tex
template waveform --> template
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1027 ccdd05d5-56c1-461a-bf98-85f6876523b4

Here we describe a method for reducing the computational cost of a \TD\ search
for compact binary coalescence.  We give a truly zero-latency algorithm
that competes in terms of floating point operations per second with the
conventional \FD\ method, which by contrast requires a significant latency due to the
inherent acausality of the Fourier transform.  Our method, called \lloid{}
(a backronym for Low Latency Online Inspiral Detection),
involves two transformations of the template waveforms that produce a
network of orthogonal filters that is far more computationally
efficient than the original bank of matched filters.

@@

\subsection{Selectively reducing the sample rate of the data and template waveforms}

>>>>

Here we describe a method for reducing the computational cost of a \TD\ search
for compact binary coalescence.  We give a truly zero-latency algorithm
that competes in terms of floating point operations per second with the
conventional \FD\ method, which by contrast requires a significant latency due to the
inherent acausality of the Fourier transform.  Our method, called \lloid{}
(a backronym for Low Latency Online Inspiral Detection),
involves two transformations of the templates that produce a
network of orthogonal filters that is far more computationally
efficient than the original bank of matched filters.

@@

\subsection{Selectively reducing the sample rate of the data and templates}
